Community Embeddings for Facebook Friend Suggestions\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2020-10-14 paper-ffs.tex
figure1 should be on page 1

\begin{abstract}
    Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
    Recommender systems are used in a wide range of business applications and are essential for online, e-business models to survive and strive in the contemporary market. Using graph embeddings for recommendation tasks has the possibility of improving upon recommender systems, because of data compression, the feature vector format, and sub-quadratic time complexity on computing embeddings.
    Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions. ComE BGMM+VI is an alteration of the community embeddings algorithm ComE. ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
    Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized hit-rate of 32.9\% is presented.
\end{abstract}

@@

This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions. Graph and community embeddings generated with ComE BGMM+VI are used to develop a friend suggestions recommender system based on the shortest distances between nodes in the embedding. Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.

>>>>

\begin{abstract}
    Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
    Recommender systems are used in a wide range of business applications and are essential for online e-business models to survive and strive in the contemporary market. Using graph embeddings for recommendation tasks can improve upon recommender systems because of data compression, the feature vector format, and sub-quadratic time complexity on computing embeddings.
    Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions. ComE BGMM+VI is an alteration of the community embeddings algorithm ComE. ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
    Recommendations are evaluated by the top-N hit-rate for users with at least 50 friends. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized hit-rate of 32.9\% is presented.
\end{abstract}

@@

This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions. Graph and community embeddings generated with ComE BGMM+VI\footnote{The ComE BGMM+VI source code and the code used to generate friend suggestions is published at \url{https://github.com/abegehr/ComE_BGMM} \cite{ComE_BGMM_GH}.} are used to develop a friend suggestions recommender system based on the shortest distances between nodes in the embedding. Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges. A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
